Convex optimisation in communications with \texttt{cvxpy}

### 2017-07-18 article_cvxpy.tex
Tim edits following meet with Rob

\title{Convex optimisation in communications with \texttt{cvxpy}}
\author{Robert P.~Gowers}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Sami C.~Al-Izzi}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Timothy M.~Pollington}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Roger J.~W.~Hill}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Keith Briggs}
\affiliation{BT, Adastral Park}

\maketitle
% -----

@@

Here we show that an interesting problem in communications has a convex formulation that can be easily implemented computationally using the \texttt{cvxpy} \textit{Python} module. This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering.

@@

\section{Outlook}
The authors hope that this article shows the utility of \texttt{cvxpy} for simple ``toy'' problems of real-world relevance. We believe it is an invaluable resource for researchers wanting test the applicability of convex optimisation in new fields.

The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.

@@

%\section{Further applications}
\subsection*{Acknowledgements and appendix}
We would like to thank S. Johnson and S. Diamond for helpful discussions. Full code for other communication examples can be found at\\ https://github.com/cvxgrp/cvxpy/tree/master\\/examples/communications.

>>>>

\title{Convex optimisation in communications with \texttt{cvxpy}}
\author{Robert P.~Gowers}%
\author{Sami C.~Al-Izzi}%
\author{Timothy M.~Pollington}%
\author{Roger J.~W.~Hill}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Keith Briggs}
\affiliation{BT, Adastral Park}
\maketitle

% -----

@@

Here we show that an interesting problem in communications has a convex formulation that can be easily implemented computationally using the \texttt{cvxpy} \textit{Python} module. This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering. First let us introduce some basic convexity concepts.

@@

\section{Outlook}
The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance. We believe it is an invaluable resource for researchers wanting test the applicability of convex optimisation in new fields.

The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation. Full code for other communication examples can be found at https://github.com/cvxgrp/cvxpy/\\tree/master/examples/communications.

@@

%\section{Further applications}
\subsection*{Acknowledgements}
We would like to thank S.~Johnson from MathSys and S.~Diamond for helpful discussions.
